Using Fundamental Measure Theory to treat the two-point pair distribution function of the Inhomogeneous Hard-Sphere Fluid

### 2013-06-26 papers/pair-correlation/paper.tex

\section{What is our new idea?}

\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/ghs-g}
  \includegraphics[width=3cm]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\subsection{Pair distribution function}
Figure~\ref{fig:pair-distribution} shows...
\begin{figure}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-0.pdf}
  \includegraphics[width=6cm]{figs/pair-correlation-2-395-5.pdf}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-10.pdf}
  \caption{Plot of the pair distribution function near a hard wall.
    In the interest of space and memeory, we should look at the function and decided which data to add?}\label{fig:pair-distribution}
\end{figure}

>>>>

\section{What is our new idea?}
We approximate the pair correlation with the average of two radial
distribution functions, evaluated at the distance between the two
points, that are themselves functions of our published pair
correlation at contact $g_{sigma}$ evaluated at the two points.

\begin{dmath}
  g^{(2)}(\rr_1,\rr_2) = \frac{g(|r_{12}|, g_\sigma(\rr_1)) + g(|r_{12}|, g_\sigma(\rr_2))}{2}
\end{dmath}

In the previous approaches mentioned above, function forms of radial
distributions (used to approximate pair correlation) were dependent
upon independent variables $\eta$, the density, wether at single
points or averaged over sourrounding volumes.  We can achieve more
accuracy by using instead a function dependent upon our $g_{\sigma}$,
which holds more information about an inhomogeneous system
then an average $\eta$ does.  We therefore need a function form for
our radial distribution that is dependent upon $g_{\sigma}$ and that
will approach the correct solution in the homogeneous limit and also
in the limit of contact distance between the two points.

The demand that our solution is correct in the homogeneous limit forms
the basis of the derivation of our radial distribtuion's function
form. We use the well known and very successful Carnahan Starling
equation to calculated $g_{\sigma}$ and then simple monte-carlo
simulations to calculate values of the homogeneous radial distribution
function at varying distance perameter $r$ (Our previously published
$g_{\sigma}$ approaches the Carnahan Starling version in the
homogeneous limit and it's simplest to use an analytical expression
for this calculation).  We then construct our radial distribution
function that has the form of an expansion of powers of $h_{\sigma} =
g_{\sigma}-1$ and perform a least squares fit to the monte-carlo
solution to find the needed constant perameters.  The function is
constructed in such a way as to appoach $g_{\sigma}$ in the limit of
contact distance between the particles.  After this process we have a
radial distribution function that is dependent only on $g_{\sigma}$
and that gives the correct solution in the homogeneous and contact
distance limit.

The function has the form:

\begin{align}
  g(|\rr|) = 1 + g_{sigma}e^{-x_0r} + x_1g_{sigma}sin(x_2r)e^{-x_3r} -x_4g_{sigma}^2sin(x_5r)e^(-x_6r)
\end{align}

The finalalized form of our pair correlation function is:

\begin{dmath}
  g^{(2)}(\rr_1,\rr_2) = \frac{g(|r_{12}|, g_\sigma(\rr_1)) + g(|r_{12}|, g_\sigma(\rr_2))}{2}
\end{dmath}

%% gsigma = gsigconcatenated[i] - 1
%%         h0 = gsigma # was x[0]*gsig
%%         f0 = numpy.exp(-x[0]*rconcatenated[i])
%%         h1 = x[1]*gsigma
%%         f1 = numpy.sin(x[2]*rconcatenated[i]) * numpy.exp(-x[3]*rconcatenated[i])
%%         h2 = -x[4]*gsigma**(2)
%%         f2 = numpy.sin(x[5]*rconcatenated[i]) * numpy.exp(-x[6]*rconcatenated[i])
%%         g[i] = 1 + h0*f0 + h1*f1 + h2*f2
%%     return g

%% The homogeneoues limit $g_{sigm}$ can be calculated using the well
%% known and very successful Carnahan Starling equation while the
%% homogeneous limit radial distribution function can be calculated using
%% Monte-Carlo methods.  We used these calculations in a least squares
%% fit along the data points at increasing radial distances in order to
%% fit the perameters of our more general pair correlation function.  Our
%% function will therefore approach the most accurate solution possible
%% in the homogeneous limit.  Created a function that has the form of an
%% expansion in powers of $g_{sigma}$.  $g_{sigm}$ in the homogeneous
%% limit can be calculated using the well known and very successful
%% Carnahan Starling equation.  has a well known and Perameters in the
%% expansion where fit
\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
Figure~\ref{fig:radial-distribution} shows...
\begin{figure}
  \includegraphics[width=3cm]{figs/ghs-g}
  \includegraphics[width=3cm]{figs/ghs-g-ghs}
  \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
\end{figure}
\subsection{Pair distribution function}
Figure~\ref{fig:pair-distribution} shows...
\begin{figure}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-0.pdf}
  \includegraphics[width=6cm]{figs/pair-correlation-2-395-5.pdf}
  %%\includegraphics[width=6cm]{figs/pair-correlation-2-395-10.pdf}
  \caption{Plot of the pair distribution function near a hard wall.
    In the interest of space and memeory, we should look at the function and decided which data to add?}\label{fig:pair-distribution}
\end{figure}
